---
title: "assignment_1_angelo_barisano"
output: html_document
date: '2022-09-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


Please note: I have used an autoformatter which I built years ago

```{r import data & set wkdir}

# clear environment
rm(list=ls())

setwd("/home/angelo/Documents/Uni/Courses/Advanced Statistics and programming/Assignments/assignment1")

df <- read.csv("Data/train.csv", header= TRUE, sep= ",")

```

```{r Initial data inspection}
View(df)
str(df)
```


```{r fix dtype}
# this is a saveguard as integer operation wont work on this column if i make a mistake
df$Id <- as.character(df$Id)

# MSSubClass is a CLASS of buildings
df$MSSubClass <- as.factor(df$MSSubClass)
df$MSZoning <- as.factor(df$MSZoning)
df$Street <- as.factor(df$Street)
df$Alley <- as.factor(df$Alley)
df$LotShape <- as.factor(df$LotShape)
df$LandContour <- as.factor(df$LandContour)
df$Utilities <- as.factor(df$Utilities)
df$LotConfig <- as.factor(df$LotConfig)
df$LandSlope <- as.factor(df$LandSlope)
df$Neighborhood <- as.factor(df$Neighborhood)
df$Condition1 <- as.factor(df$Condition1)
df$Condition2 <- as.factor(df$Condition2)
df$BldgType <- as.factor(df$BldgType)
df$HouseStyle <- as.factor(df$HouseStyle)

# question: is overall quality (OverallCond and OverallQual)interval of ordinal?
# df$OverallQual <- as.factor(df$OverallQual)
# df$HouseStyle <- as.factor(df$OverallCond)

# years built is an ordinal/ or nominal variable; so I will put into a factor
#NOTE: YEAR and timesince can function as a variable here! conidering the YearRemodAdd (remodel date)
df$YearBuilt <- as.factor(df$YearBuilt)
df$YearRemodAdd <- as.factor(df$YearRemodAdd)

df$RoofStyle <- as.factor(df$RoofStyle)
df$RoofMatl <- as.factor(df$RoofMatl)
df$Exterior1st <- as.factor(df$Exterior1st)
df$Exterior2nd <- as.factor(df$Exterior2nd)
df$MasVnrType <- as.factor(df$MasVnrType)
df$ExterQual <- as.factor(df$ExterQual)
df$ExterCond <- as.factor(df$ExterCond)
df$Foundation <- as.factor(df$Foundation)
df$ExterCond <- as.factor(df$ExterCond)
df$Foundation <- as.factor(df$Foundation)
df$BsmtQual <- as.factor(df$BsmtQual)
df$BsmtCond <- as.factor(df$BsmtCond)
df$BsmtExposure <- as.factor(df$BsmtExposure)
df$BsmtFinType1 <- as.factor(df$BsmtFinType1)
df$BsmtFinType2 <- as.factor(df$BsmtFinType2)

df$Heating <- as.factor(df$Heating)
df$HeatingQC <- as.factor(df$HeatingQC)
df$CentralAir <- as.factor(df$CentralAir)
df$KitchenQual <- as.factor(df$KitchenQual)
df$Functional <- as.factor(df$Functional)
df$FireplaceQu <- as.factor(df$FireplaceQu)
df$GarageType <- as.factor(df$GarageType)
df$GarageYrBlt <- as.factor(df$GarageYrBlt)
df$GarageFinish <- as.factor(df$GarageFinish)

# GARAGE TYPE MAY BE A GOOD VARIABLE AS THE SIZE MEANS MORE CARS AND MORE CARS MEANS RICHER PEOPLE!!!
df$GarageCars <- as.factor(df$GarageCars)

df$GarageQual <- as.factor(df$GarageQual)
df$GarageCond <- as.factor(df$GarageCond)
df$PavedDrive <- as.factor(df$PavedDrive)
df$PoolQC <- as.factor(df$PoolQC)


df$Fence <- as.factor(df$Fence)
df$MiscFeature <- as.character(df$MiscFeature)



# IMPORTANT FEATURES
# put month as factor; convert it properly to character type
df$MoSold <- as.factor(df$MoSold)
df$YrSold <- as.factor(df$YrSold)

# this one is interesting
df$SaleType <- as.factor(df$SaleType)
# this one just to make it clear
df$SalePrice <- as.integer(df$SalePrice)


```





``` {r select variables for analysis}







```



# Generally helpful variables
Number ofbedrooms and bathrooms
overall size
years since remodeling
years since build 
how many spots in the garage 

# ALSO! If a house was sold multiple times, this would imply a cluster by house; or possibly by area as well; so this is interesint wrt the standard error of the eestimated parameters !!!

# relevant variables:
SalePrice

# class of the building 
MSSubClass,
BldgType ---> eg one family home etc,

# area in city/ district
MSZoning,
Neighborhood: Physical locations within Ames city limits

# size of the property 
LotArea --> size of the overall lot/ property,


# overall quality contains the overall quality of the house and the condition together 
# IMPORTANT! Is the degree of finish of the house here/ i mean: is the house really finished and is this reflected in this variable?
OverallQual -- overall quality,
OverallCond --> overall condition of the house,

# age and need or remodeling of he house inpsulateded here 
YearBuilt,
YearRemodAdd,

# heating overall
HeatingQC
CentralAir
Electrical

# size of the house
1stFlrSF: First Floor square feet
2ndFlrSF: Second floor square feet

# nuber of bathrooms
BsmtFullBath: Basement full bathrooms
BsmtHalfBath: Basement half bathrooms
FullBath: Full bathrooms above grade
HalfBath: Half baths above grade

Bedroom: Number of bedrooms above basement level
Kitchen: Number of kitchens

Functional: Home functionality rating


GarageCars: Size of garage in car capacity
GarageArea: Size of garage in square feet

# sales features
MoSold: Month Sold
YrSold: Year Sold
SaleType: Type of sale
SaleCondition: Condition of sale

 
 
 
 
 
 

```{r missing values inspection}
# display missing values by column
colSums(is.na(df))

# select all columns which have missing data 
which(colSums(is.na(df))>0)

NONE
```







Data fields
Here's a brief version of what you'll find in the data description file.

SalePrice - the property's sale price in dollars. This is the target variable that you're trying to predict.
MSSubClass: The building class
MSZoning: The general zoning classification
LotFrontage: Linear feet of street connected to property
LotArea: Lot size in square feet
Street: Type of road access
Alley: Type of alley access
LotShape: General shape of property
LandContour: Flatness of the property
Utilities: Type of utilities available


LotConfig: Lot configuration
LandSlope: Slope of property
Neighborhood: Physical locations within Ames city limits
Condition1: Proximity to main road or railroad
Condition2: Proximity to main road or railroad (if a second is present)
BldgType: Type of dwelling
HouseStyle: Style of dwelling
OverallQual: Overall material and finish quality
OverallCond: Overall condition rating
YearBuilt: Original construction date
YearRemodAdd: Remodel date
RoofStyle: Type of roof
RoofMatl: Roof material
Exterior1st: Exterior covering on house
Exterior2nd: Exterior covering on house (if more than one material)
MasVnrType: Masonry veneer type
MasVnrArea: Masonry veneer area in square feet
ExterQual: Exterior material quality
ExterCond: Present condition of the material on the exterior
Foundation: Type of foundation
BsmtQual: Height of the basement
BsmtCond: General condition of the basement
BsmtExposure: Walkout or garden level basement walls
BsmtFinType1: Quality of basement finished area
BsmtFinSF1: Type 1 finished square feet
BsmtFinType2: Quality of second finished area (if present)
BsmtFinSF2: Type 2 finished square feet
BsmtUnfSF: Unfinished square feet of basement area
TotalBsmtSF: Total square feet of basement area
Heating: Type of heating
HeatingQC: Heating quality and condition
CentralAir: Central air conditioning
Electrical: Electrical system
1stFlrSF: First Floor square feet
2ndFlrSF: Second floor square feet
LowQualFinSF: Low quality finished square feet (all floors)
GrLivArea: Above grade (ground) living area square feet
BsmtFullBath: Basement full bathrooms
BsmtHalfBath: Basement half bathrooms
FullBath: Full bathrooms above grade
HalfBath: Half baths above grade
Bedroom: Number of bedrooms above basement level
Kitchen: Number of kitchens
KitchenQual: Kitchen quality
TotRmsAbvGrd: Total rooms above grade (does not include bathrooms)
Functional: Home functionality rating
Fireplaces: Number of fireplaces
FireplaceQu: Fireplace quality
GarageType: Garage location
GarageYrBlt: Year garage was built
GarageFinish: Interior finish of the garage
GarageCars: Size of garage in car capacity
GarageArea: Size of garage in square feet
GarageQual: Garage quality
GarageCond: Garage condition
PavedDrive: Paved driveway
WoodDeckSF: Wood deck area in square feet
OpenPorchSF: Open porch area in square feet
EnclosedPorch: Enclosed porch area in square feet
3SsnPorch: Three season porch area in square feet
ScreenPorch: Screen porch area in square feet
PoolArea: Pool area in square feet
PoolQC: Pool quality
Fence: Fence quality
MiscFeature: Miscellaneous feature not covered in other categories
MiscVal: $Value of miscellaneous feature
MoSold: Month Sold
YrSold: Year Sold
SaleType: Type of sale
SaleCondition: Condition of sale








```{r Data cleaning and imputation}
# Missing Value Treatment
for(i in c(1:78))
{
  if(class(train[,i])=="factor")
  {
    train[is.na(train[,i]),i]<-names(which.max(table(train[,i])))
  }else{
    train[is.na(train[,i]),i]<-median(unlist(train[,i]),na.rm = TRUE)
  }
}

```







## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
